### 2020-06-01 writeup/experiments.tex

\textbf{Baseline.} We compare Algorithm \ref{alg_inc_train} to a model trained with standard multi-task learning approaches.

@@

\textbf{Improving multi-task training efficiency.}
We compare Algorithm \ref{alg_inc_train} to performing multi-task learning.
Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the cost to achieve the same performance on the target task, compared to multi-task learning.

>>>>

\textbf{Baseline.} We compare Algorithm \ref{alg_inc_train} to a model trained with standard multi-task learning approaches.
We measure the prediction accuracy of a particular target task.

@@

\textbf{Improving multi-task training efficiency.}
We compare Algorithm \ref{alg_inc_train} to performing multi-task learning.
Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.

### 2020-06-01 writeup/proof_examples.tex

\subsection{Supplement to Section \ref{sec_datasize}} \label{app_proof_32}
We first prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.

>>>>

\subsection{Supplement to Section \ref{sec_data_size}} \label{app_proof_32}
We first prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.
